---
title: "Getting started with altdown"
vignette: >
  %\VignetteIndexEntry{Getting started with altdown}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

This vignette shows off a few Quarto callout blocks, and how they render
on a site built with `altdoc`'s `quarto_website` tool, which lets Quarto
handle vignettes directly instead of converting them to plain Markdown
first.

`greet()` and `add()` below are not part of the real package API; they
are toy functions injected during the site build for this showcase (see
the [reference index](../reference.qmd)).

```{r setup}
library(altdown)
```

## Saying hello

::: {.callout-note}
`greet()` is a toy demo function; it just pastes together a friendly
string. Nothing fancy.
:::

```{r}
greet("altdoc")
```

You can also shout the greeting:

```{r}
greet("altdoc", loud = TRUE)
```

::: {.callout-tip}
## Tip
Set `loud = TRUE` when you really mean it.
:::

## Adding numbers

```{r}
add(2, 40)
```

::: {.callout-warning}
Like `greet()`, `add()` is a toy stand-in: it does no input validation,
so passing non-numeric arguments raises a base R error rather than a
friendly one.
:::

```{r, error=TRUE}
add("2", 40)
```
