---
title: "Getting started with altdown"
vignette: >
  %\VignetteIndexEntry{Getting started with altdown}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

This vignette shows off the two toy functions in the package, and a few
Quarto callout blocks along the way. Callouts like these render natively
because this site is built with `altdoc`'s `quarto_website` tool, which
lets Quarto handle vignettes directly instead of converting them to plain
Markdown first.

```{r setup}
library(altdown)
```

## Saying hello

::: {.callout-note}
`greet()` just pastes together a friendly string. Nothing fancy.
:::

```{r}
greet("altdoc")
```

You can also shout the greeting:

```{r}
greet("altdoc", loud = TRUE)
```

::: {.callout-tip}
## Tip
Set `loud = TRUE` when you really mean it.
:::

## Adding numbers

```{r}
add(2, 40)
```

::: {.callout-warning}
`add()` does no input validation, so passing non-numeric arguments will
raise a base R error rather than a friendly one.
:::

```{r, error=TRUE}
add("2", 40)
```

::: {.callout-important}
This package is a toy, built only to demonstrate `altdoc` and Quarto
callout blocks alongside pkgdown-style theming. Don't expect real
functionality here.
:::
